---
title: "RWorksheet_Lomibao#3b"
author: "lomibao"
date: "2024-10-03"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1.A
```{r}

dataf <- data.frame(
  Respondents = c(1:20),
  Sex = c(2, 2, 1, 2, 2, 2, 2, 2, 2, 2, 1, 2, 2, 2, 2, 2, 2, 2, 1, 2),
  Fathers_Occupation = c(1, 3, 3, 3, 1, 2, 3, 1, 1, 1, 3, 2, 1, 3, 3, 1, 3, 1, 2, 1) ,
  Persons_at_Home =  c(5, 7, 3, 8, 5, 9, 6, 7, 8, 4, 7, 5, 4, 7, 8, 8, 3, 11, 7, 6),
  Siblings_at_School =  c(6, 4, 4, 1, 2, 1, 5, 3, 1, 2, 3, 2, 5, 5, 2, 1, 2, 5, 3, 2),
  Types_of_Houses = c(1, 2, 3, 1, 1, 3, 3, 1, 2, 3, 2, 3, 2, 2, 3, 3, 3, 3, 3, 2)
)
dataf
```
B.It shows the summary of the data such as mean, median, max, min and etc. 
```{r}
summary(dataf)
```
C. No its 2.95. You could see it at the data itself.
D.
```{r}
subf <- dataf[1:2 , ]
subf
```
E.
```{r}
ot_subf <- dataf[c(3,5) , c(2,4)]
ot_subf
```
F.
```{r}
types_houses <- dataf[ , "Types_of_Houses"]
types_houses
```
G.
```{r}
mal_res <- subset(dataf, Sex == 1 & Fathers_Occupation == 1)
mal_res
```
H.
```{r}
fem_res <- subset(dataf, Sex ==2 & Siblings_at_School >=5)
fem_res
```
2.It show what is within the dataframe such as objects, variables and data types.
```{r}
df = data.frame(Ints=integer(),

Doubles=double(), Characters=character(),
Logicals=logical(),
Factors=factor(),
stringsAsFactors=FALSE)

print("Structure of the empty dataframe:")
print(str(df))
```
3.A.
```{r}
HouseholdData <- read.csv("/cloud/project/HouseholdData - Sheet1.csv")
HouseholdData

```
B.
```{r}
HouseholdData$Sex <- factor(HouseholdData$Sex, levels = c("Male","Female"), labels = c(1,2))
HouseholdData
```
C.
```{r}
HouseholdData$Types_of_houses <- factor(HouseholdData$Types_of_houses, levels = c("Wood", "Congrete", "Semi-congrete"), labels = c(1, 2, 3))
HouseholdData
```
D.
```{r}
HouseholdData$Fathers_Occupation <- factor(HouseholdData$Fathers_Occupation, levels = c(1, 2, 3), labels = c("Farmer", "Driver", "Others"))
HouseholdData
```
E.
```{r}
female_res <- subset(HouseholdData, Sex==2 & Fathers_Occupation =="Driver")
female_res
```
F.
```{r}
ms <- subset(HouseholdData, Respondents & Siblings_at_schools >=  5)
ms
```
4.
The graph show the sentiment of tweets from July 14, 2020 to July 21 ,2020. It shows that negative and neutral Tweets reach their peaks in July 15,2020 While the positive tweets reach their peaks in July 21, 2020. 