---
title: "RWorksheet_Lomibao4c"
author: "lomibao"
date: "2024-11-04"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

```
1.A
```{r}
mpg_ds <- read.csv("/cloud/project/mpg.csv")
mpg_ds
 # str(mpg_ds)
```
For B and C I use str() to gather the data but i comment it out to minimize the space for knitting. 

B.The categorical variables are manufacture, model,types of transmission,drive-type,fuel type, number of cylinders and vehicle class. 

C.The continuous variables are engine displacement, year of manufacturing,city mileage, and highway mileage.
2.
Top manufacturer is toyota and top model is caravan 2wd.
```{r}
library(dplyr) #install the package dplyr and load the package
library(ggplot2) #load the ggplot2 package


manufacturer_count <- mpg_ds %>%
  group_by(manufacturer) %>%
  summarise(model_count = n_distinct(model)) %>%
  arrange(desc(model_count))

top_manufacturer <- manufacturer_count[1, ]

model_variation <- mpg_ds %>%
  group_by(model) %>%
  summarise(variation_count = n()) %>%
  arrange(desc(variation_count))

top_model <- model_variation[1, ]

top_manufacturer
top_model
```
A.
```{r}
  mu <- mpg_ds %>%
  group_by(manufacturer) %>%
  summarise(unique_models = n_distinct(model)) %>%
  arrange(desc(unique_models))
mu
```
B.for plot()
```{r}
library(dplyr)
barplot(mu$unique_models, 
        names.arg = mu$manufacturer, 
        col = "green",
        main = "Unique Models per Manufacturer", 
        xlab = "Manufacturer", 
        ylab = "Number of Unique Models",
        las = 2,          
        cex.names = 0.7
        )
```
for  ggplot()
```{r}
library(ggplot2)

ggplot(mu, aes(x = manufacturer, y = unique_models)) +
  geom_bar(stat = "identity", fill = "blue") +
  ggtitle("Unique Models per Manufacturer") +
  xlab("Manufacturer") +
  ylab("Number of Unique Models") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 10)) 
```
2.2 The code show a scatter plot about data and the relationship between the car manufacturer and the model but dataset seems have a lot of data it looks a little bit crowded.
```{r}
ggplot(mpg, aes(model, manufacturer)) + geom_point()
```
B. No and here's how.
```{r}
library(ggplot2)
library(dplyr)


mpg_top20 <- mpg %>% head(20)

ggplot(mpg_top20, aes(x = model, y = year)) +
  geom_point(color = "red", size = 3) +
  labs(title = " Model vs Year (Top 20 Observations)", 
       x = "Model", 
       y = "Year") 


```

