---
title: "RWorksheet_Lomibao#2"
author: "lomibao"
date: "2024-09-29"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}

```
1.A
```{r}
z <- -5:5
z
```
1.B - The value of x is [1] 1 2 3 4 5 6 7
```{r}
x <- 1:7
x
```
2.A - The output is the sequence of 1 to 3 but with 0.2 interval.
```{r}
seq(1,3, by=0.2)
```
3
```{r}
age <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35, 24, 33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18)
Third_element <- age[3]
Third_element
```
A. The third element is 22

```{r}
second_fourth <- age[c(2, 4)]
second_fourth
```
B.The second and fourth values is 28, and 36
C.
```{r}
age[-c(4, 12)]
```
4.
```{r}
x <-c("first" = 3,"second"=0, "third"=9)

```
A.When I print the vector it shows the columns names ("first","third") and their assign values.
```{r}
x [c("first", "third")]
```
B.
```{r}
x <-c("first" = 3,"second"=0, "third"=9)
x
```
5.A. The codes works but the second elements that must be -2 became 0.
```{r}
x <- -3:2
x[2] <-0
x
```
B.
```{r}
x <- -3:2
x[2] <-0
x
```
6.A
```{r}
MrCruzFuelData <- data.frame(
    Month = c("Jan", "Feb", "Mar", "Apr", "May", "Jun"),
    Price_per_Liter= c(52.50, 57.25, 60.00, 65.00, 74.25, 54.00),Purchase_quantity= c(25, 30, 40, 50, 10, 45)
)
MrCruzFuelData
```
B.The average fuel expenditure is 59.26.
```{r}
avg_fuel <- weighted.mean(MrCruzFuelData$Price_per_Liter, MrCruzFuelData$Purchase_quantity)
avg_fuel
```
7.A.
```{r}
rivers
riv_data <- c(length(rivers), sum(rivers), mean(rivers), median(rivers), var(rivers), sd(rivers), min(rivers), max(rivers))
riv_data
```
B.The output are it prints the length, sum, mean, median, variance, standard deviation, minimum, and maximum of the rivers.
c.
```{r}
riv_data <- c(length(rivers), sum(rivers), mean(rivers), median(rivers), var(rivers), sd(rivers), min(rivers), max(rivers))
riv_data
```
8.A.
```{r}

PowerRanking <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25)
CelebrityName <- c("Tom Cruise", "Rolling Stones", "Oprah Winfrey", "U2", "Tiger Woods", "Steven Spielberg", "Howard Stern", "50 Cent", "Cast of the Sopranos", "Dan Brown", "Bruce Springsteen", "Donald Trump", "Muhammad Ali", "Paul McCartney", "George Lucas", "Elton John", "David Letterman", "Phil Mickelson", "J.K. Rowling", "Brad Pitt", "Peter Jackson", "Dr. Phil McGraw", "Jay Leno", "Celine Dion", "Kobe Bryant")
Pay <- c(67, 90, 225, 110, 90, 332, 302, 41, 52, 88, 55, 44, 55, 40, 233, 34, 40, 47, 75, 25, 39, 45, 32, 40, 31)
PowerRanking
CelebrityName
Pay
```
B.
```{r}
Rowling <- which(CelebrityName == "J.K. Rowling") 
PowerRanking[Rowling] <- 15
Pay[Rowling] <- 90
PowerRanking
Pay
```
C.
```{r}
forbes <- read.csv("/cloud/project/Power Ranking - Sheet1.csv")
```
D.
```{r}
ranks <- forbes[10:20,]
ranks
save(ranks, file = "/cloud/project/Power Ranking - Sheet1.csv" )
```
E.The output shows that it prints celebrities starting from ranked 10 to 20 with their pay and names.

9.A
```{r}
library("openxlsx")
library("readxl")

hotelsvienna <- read_xlsx("/cloud/project/hotels-vienna.xlsx")
```
B.It has 428 row dimensions and 24 column dimensions
```{r}
dim(hotelsvienna)
```
c.
```{r}
column <- hotelsvienna[, c("country","neighbourhood", "price","stars","accommodation_type","rating")]
```
D.
```{r}
save(column, file ="/cloud/project/new.RData")
```
e.
```{r}
load("/cloud/project/new.RData")
head(column, 6)
tail(column, 6)
```
10.A
```{r}
vegetables <- list("Carrots", "Potato", "Tomatoes", "Eggplant", "Garlic", "Raddish", "Cabbage", "Chili", "Onion", "String Beans" )
vegetables
```
B.
```{r}
vegetables <- append(vegetables, list("moringa", "black beans"))
vegetables
```
C.There are 16 data points in vegetables list.
```{r}
vegetables <- append(vegetables, list("Corn", "Pumpkin", "Ginger", "Leek"))
vegetables
length(vegetables)
```
D.There were 13 vegetables left.
```{r}
vegetables <- vegetables[-c(5, 10, 15)]
vegetables
```

